---
title: "POC"
output: html_document
---

```{r}
#Importing data
 library(dplyr)
data.org <- read.csv(file.choose(), stringsAsFactors = T)

```
 ## loaded the dataset 

```{r}
#Finding missing values
sort(colSums(is.na(data.org)),decreasing = TRUE)

```

 ## Checking the missing values and arranged in the increasing order

```{r}

#Removing variables having missing values more than 30%
data.org <- data.org[, c(-242,-295,-304,-098,-155,-259,-255,-256,-257,-302,-268,-162,-265,-266,-267,-253,-297,-275,-293,-288,-289,-290,-148,-223,-222,-041,-057,-058,-237,-238,-239)]

```                     

 ## And removing variables morethan 30% missing values variables in the dataset 

```{r}

#Removing missing values having unique value
which(colnames(data.org) == 'x067')
which(colnames(data.org) == 'x094')
which(colnames(data.org) == 'x095')
which(colnames(data.org) == 'x096')
which(colnames(data.org) == 'x276')

```

 ## Checking the index numbers of variables in the dataset

```{r}

#Removing missing values having unique value
data.org <- data.org[, c(-64,-91,-92,-93,-253)]
 
```

 ## removing unique value variables in the dataset
 

```{r}
 #Taking 5000 observations from the dataset 
data.999 <- sample_n(data.org,5000)
```

 ## Taking 5% sample from the dataset 

```{r}
#importing the values with 999
library(dplyr)
data.999 <- mutate_all(data.999, funs(replace(., is.na(.), 999)))
```

 ## Imputing missing values with 999 

```{r}
# install.packages('randomForest')
library(randomForest)
set.seed(1234)
regressor <- randomForest(x= data.999[-269],
                          y = data.999$y,
                          ntree = 57)

#Predicting results
rf_pred  = predict(regressor, newdata = data.999)

```

 ## checking accuracy of the sample data 
 

```{r}
#Calculate RMSE 
# summarize accuracy
rmse <- sqrt(mean((data.999$y - rf_pred)^2))

```

 ## And i observed 14% error in the data set using with random forest



```{r}
#SVM 
#install.packages("e1071")
library(e1071)
svm_regressor = svm(formula = y ~ .,
                    data = data.999,
                    type = 'eps-regression',
                    kernel = 'radial')

#Predicting results
svm_pred  = predict(svm_regressor, newdata = data.999)
```

 ## Checking accuracy of sample data using with  SVM 

```{r}
#Calculate RMSE 
# summarize accuracy
rmse <- sqrt(mean((data.999$y - rf_pred)^2))                 
```
 
 ## Observation
 
 I observed 14% error in the sample data
 And I taken 5% of whole dataset and i observed 14% of error ,using with SVM and random forest
